Local PCA results

### 2016-12-15 medicago/medicago_data_setup.Rmd
minor notes

>>>>

## Weights

To check the effect of subsampling,
here's a way to make a file of weights:
```{r make_weights}
samples$nsamples <- table(samples$Country.of.Origin)[samples$Country.of.Origin]
samples$weight <- 1/pmax(10,samples$nsamples)

bcf.samples <- vcf_samples("data/chr1-filtered-set-2014Apr15.bcf")
bcf.samples[bcf.samples=="HM020-I"] <- "HM020"

weights <- data.frame( ID=bcf.samples, weight=samples$weight[match(bcf.samples,samples$ID)] )

write.table(weights, sep="\t", file="data/inverse-samplesize-weights.tsv", row.names=FALSE)
```

## Gene location information

Non-TE related gene data downloaded from [jcvi.org's JBrowse](http://jcvi.org/medicago/jbrowse/?data=data%2Fjson%2Fmedicago&loc=chr1%3A9010377..51403300&tracks=gene_models&highlight=) on 4 September 2015.
